Exploration of ED outputs

### 2019-02-13 analysis/paper/exploratory.Rmd
Add LAI by PFT ensemble analysis

@@

>>>>

# Summary of output

@@

# LAI, by ensemble member

Load the LAI output (generated by script `analysis/scratch/read_ed_lai.R`).

```{r load-lai}
lai_file <- here::here("analysis/data/derived-data/ed-lai-output.fst")
all_lai <- fst::read_fst(lai_file)
```

Calculate annual maximum and plot.

```{r lai-ensemble-plot}
all_lai %>%
  group_by(year = lubridate::floor_date(month, "year"),
           pft, ensemble) %>%
  summarize(lai = max(lai)) %>%
  ungroup() %>%
  filter(pft != "Late conifer") %>%
  ggplot() +
  aes(x = year, y = lai, color = pft) +
  geom_line() +
  facet_wrap(~ensemble)
```
